Data Structures Comparative Review Thing

### 2014-04-16 paper/paper.tex
minor change
my dad teaches english and corrected me here (on my request)
Wrote the introduction and started on the conclusion.

    \section{Introduction}

    We did research about what data structure could best be used to represent a blacklist in a 
    web-filter application.  We compared the insertion speed, query speed, and memory usage of three
    data structures: the binary search tree, the hash table, and the skip list.  We did this because
    we really liked these three structures.

    \section{Implementation}
    \subsubsection*{Datastructures}

@@

    \subsubsection*{Data}
    For our data, we took the system's dictionary file and the list of top level domains from Wikipedia
    and combined these to generate a list of items in the form \texttt{www.\$word.\$tld}, where
    \texttt{\$word} is one of words from the the dictionary and \texttt{\$tld} is a top level domain.  Only
    words consisting of the lowercase letters \texttt{a} through \texttt{z} were used.  Constraining the
    words to consist of 8 to 12 characters and limiting the top-level domains to exactly two letters, 
    all possible combinations were generated.  For the full paths, a number of domains was selected
    and each was appended a random alphanumeric string of eighty characters.  The exact implementation
    can be viewed in the sourcecode\footnote{ref to apendix or code dump}.

@@

    \section{Conclusions}

>>>>

    \section{Introduction}
    A website filter is a program that catagorises websites in order to restrict access to designated
    sites a user might visit. Commonly, the filter includes a blacklist of sites a user may not visit
    unless they have certain credentials, or alternatively, includes a whitelist so it can blacklist
    everything else. As the world-wide web is growing, these lists have grown larger to a point where
    the speed of the underlying data structure has become a key issue. The time of both inserting and
    looking up websites must be kept minimal. This all must be done without too much of a trade-off
    between speed and memory usage.

    In technical terms, we would want the best data structure for associating many URLs with their
    respective permissions, be it whitelisted or blacklisted for certain users. In researching the best
    associative data structure we have picked implementations of the binary search tree, the hash map
    and the skip list. These are the key options in such a problem. We are interested in finding which
    one would perform best under a various number of insertions. The main research question of this paper
    is as follows:

    How does the number of entries influence the performance of various associative data structures?

    While the decision of data structure might mostly be dependant on the number of entries, the complexity
    of the key might also be of concern. Where permissions per page would be preferred, a more
    resource optimal solution might be found in filtering only on domain or even IP adress.
    In researching the influence of this we formulate a secondary research question:

    How does the complexity of the key influence the preformance of various associative data structures?

    In the following paper, we will attempt to answer these questions. The next section will give details
    about our research plan and the scopes of our research. The section thereafter is about the implementation
    of our setup in C++. Next, we will state our results, after which we will discuss set results and provide
    several conclusions.    
    %We did research about what data structure could best be used to represent a blacklist in a 
    %web-filter application.  We compared the insertion speed, query speed, and memory usage of three
    %data structures: the binary search tree, the hash table, and the skip list.  We did this because
    %we really liked these three structures. 
    \section{Implementation}
    \subsubsection*{Datastructures}

@@

    \subsubsection*{Data}
    For our data, we took the system's dictionary file and the list of top level domains from Wikipedia
    and combined these to generate a list of items in the form \texttt{www.\$word.\$tld}, where
    \texttt{\$word} is one of words from the the dictionary and \texttt{\$tld} is a top level domain.  Only
    words consisting of the lowercase letters \texttt{a} through \texttt{z} were used.  Constraining the
    words to consist of 8 to 12 characters and limiting the top-level domains to exactly two letters, 
    all possible combinations were generated.  For the full paths, a number of domains were selected
    and each was appended a random alphanumeric string of eighty characters.  The exact implementation
    can be viewed in the sourcecode\footnote{ref to apendix or code dump}.

@@

    \section{Conclusions}
    Our main point of research was researching which associative data structure performed best on
    a various number of insertions, in terms of ths speed of insertions and look-ups, and memory.
    In terms of speed we can state with certainty that the hash table is the superior data structure.
    It outperforms the other two in almost every category, most significantly in larger datastructures where
    it is often takes less than half as much time as the skiplist and less than twothirds the time of the binary search tree.
    In most cases, the binary search tree is a bit slower, where the skip list is the slowest structure in
    virtually every case. The only motivation for using a hashmap for this problem appears to be in memory usage,
    although the advantage gained from this is quite small.
